### 2017-12-19 Paper/DGSM_PCE_MD_paper.tex
moved intro to a separate file

\section{Introduction}
\begin{enumerate}
\item Need for efficient Surrogates - especially for complex models to enable forward UQ, 
sensitivity studies, calibration, and experimental design (Include citations).
\item Computational Hurdles: Polynomial Chaos and GP can be computationally 
intractable and suffer from the curse of dimensionality (Include plots for PCE
to motivate dimension reduction with citations for both PCE and GP).
\item Sensitivity analyis - a potent tool for dimension reduction. However, SA can be
computationally prohibitive. In fact, there are studies demonstrating the use of 
surrogates to reduce costs associated with SA (include citations). 
\item DGSM - brief introduction and citations. 
\item Key contributions of the paper: 1) Methodology that exploits DGSM to reduce the
dimensionality of the problem and thus enables efficient construction of surrogates.
2) Application of the proposed methodology to investigate relative importance of
parameters in the stillinger-weber potential, commonly used for studying phonon transport in silicon. Further, construct a reasonably accurate PC surrogate in the reduced 
space and demonstrate computational advantage of this approach. .
\end{enumerate}

>>>>

\input{intro}
